\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}

\title{Extension and Non-Extension Rules in the COP Framework}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This document specifies the conditions under which the COP framework
may be instantiated or applied.
It also specifies explicit non-extension rules.
It introduces no new structure, notation, or claims.
Its sole purpose is to preserve structural integrity over time.
\end{abstract}

\section{Status}

This document is not descriptive.
It is disciplinarily normative.

The rules listed here are binding.
They override interpretive preference,
theoretical ambition,
and domain-specific convenience.

They do not authorize action.
They restrict use.

\section{Permitted Uses and Instantiations}

The following uses are admissible.
They do not alter the COP framework.

\subsection*{ICOP Instantiation}

ICOPs may be instantiated or referenced:
\begin{itemize}
  \item only within an existing COP--ICOP pair (1--8),
  \item without introducing new ICOP entities or labels,
  \item without modifying COP or ICOP numbering or order.
\end{itemize}

ICOPs diagnose reverse legibility.
They do not expand the framework.

\subsection*{Diagrammatic Use}

New diagrams are permitted if and only if:
\begin{itemize}
  \item they obey the grammar defined in L4,
  \item they function solely as constraint objects,
  \item they introduce no semantic interpretation or explanation.
\end{itemize}

Illustrative, explanatory, or pedagogical diagrams are inadmissible.

\subsection*{Domain Instantiation}

The COP framework may be instantiated in specific domains
(e.g.\ technical, organizational, computational)
provided that:
\begin{itemize}
  \item no domain semantics are imported into COP itself,
  \item no explanatory or predictive claims are made,
  \item admissibility remains the only operative criterion.
\end{itemize}

Instantiation is use, not modification.

\subsection*{Stress Testing}

The framework may be stress-tested via:
\begin{itemize}
  \item Shadow Axis activation,
  \item detection signals,
  \item boundary violations.
\end{itemize}

Stress tests diagnose limits.
They do not justify redesign, optimization, or repair.

\section{Forbidden Extensions}

The following moves are explicitly forbidden.

\subsection*{New COP or ICOP Entries}

No new COP or ICOP entries may be added.
This includes:
\begin{itemize}
  \item COP-09 or higher,
  \item ICOP-09 or higher,
  \item fractional, hybrid, or variant entries,
  \item redefinitions of existing COPs or ICOPs.
\end{itemize}

The operating paradox set (COP \& ICOP 1--8) is closed.

\subsection*{Reordering or Rebinding}

COP or ICOP entries may not be reordered,
regrouped,
or rebound into alternative pairings.

Any such move collapses structural constraints.

\subsection*{Semantic Enrichment}

No semantic meaning may be added to:
\begin{itemize}
  \item COP or ICOP entries,
  \item Light Axes,
  \item Shadow Axes,
  \item diagrams, states, or configurations.
\end{itemize}

Meaning is not an admissible extension.

\subsection*{Theory Construction}

The COP framework may not be turned into:
\begin{itemize}
  \item a theory of systems,
  \item a model of reality,
  \item an explanatory ontology,
  \item a predictive or optimizing mechanism.
\end{itemize}

The framework constrains admissibility.
It does not explain outcomes.

\subsection*{Shadow Instrumentalization}

Shadow Axes may not be used to:
\begin{itemize}
  \item justify intervention,
  \item derive policy,
  \item assign blame,
  \item claim authority or legitimacy.
\end{itemize}

Shadow marks limits.
It does not authorize action.

\subsection*{Framework Completion}

No move may claim that the framework is:
\begin{itemize}
  \item complete,
  \item final,
  \item total,
  \item or universally sufficient.
\end{itemize}

Any such claim violates terminal constraints (S8).

\section{Conflict Resolution}

In case of conflict:
\begin{itemize}
  \item Non-extension rules override permitted uses.
  \item Shadow Axes override Light Axes.
  \item Caps act as absolute gates and override all other sections.
\end{itemize}

No appeal beyond these constraints is admissible.

\section{Use}

Correct use of the COP framework consists in:
\begin{itemize}
  \item operating strictly within admissibility,
  \item excluding illegitimate moves,
  \item stopping when boundaries are reached.
\end{itemize}

Extension is optional.
Discipline is mandatory.

\section{Placement in the COP Corpus}

This document applies to:
\begin{itemize}
  \item the Full COP List,
  \item the Operating Paradoxes (COP \& ICOP 1--8),
  \item the Light Axes,
  \item the Shadow Axes,
  \item the Forbidden Moves Index,
  \item all future applications.
\end{itemize}

Violations do not require debate.
They require cessation.

\end{document}
