\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{COP: Core Operational Principles (00--08)}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This document presents the Core Operational Principles
(COP-00 through COP-08)
as a unified admissibility framework.
Each principle specifies structural conditions
for scalable coherence and persistence.
Known human and cosmic paradoxes
are mapped as diagnostic boundaries.
No hierarchy is imposed.
The principles function jointly as constraint architecture.
\end{abstract}

\section{COP-00: Admissibility Dominance}

Distinction is not default.
State is an event.
Null is scalable; definition is costly.

Paradox appears only where null is locally broken.

Any model that assumes ubiquitous state, value,
or distinction without accounting cost
violates scalability.

\subsection{Known Human Paradoxes}

Frame problem \\
Measurement bias \\
Overfitting \\
Model collapse \\
Map--territory confusion \\
Category error

\subsection{Known Cosmic Constraints}

Vacuum energy problem \\
Horizon problem \\
Black hole information paradox \\
Cosmic censorship (boundary logic) \\
Background independence tension

\subsection{COP Paradox}

Definition is a local scar
on a null-dominant field.

A viable system cannot keep
everything explicit.
Definition must remain local
and forced.

\section{COP-01: Redundancy Over Optimality}

Efficiency is not free.
Optimization concentrates risk.

Local extremity must be paid for
with global slack.

Failure is admissible
only if it does not propagate.

Any model relying on a single optimal channel
contradicts survivability.

\subsection{Known Human Paradoxes}

Goodhart’s Law \\
Jevons paradox \\
Cobra effect \\
Moral hazard \\
Normal accidents \\
Tight vs loose coupling \\
Second-order effects \\
Efficiency--fragility tradeoff

\subsection{Known Cosmic Constraints}

Fermi paradox \\
Black hole information paradox \\
Firewall paradox \\
Percolation thresholds \\
Fine-tuning robustness

\subsection{COP Paradox}

Optimized systems must be locally extreme
but globally redundant.

If the best path carries everything,
the system is already dead.

\section{COP-02: Multiplicity Without Totality}

Branching is admissible.
Exhaustiveness is not implied.

VEEL is not ALL.
Possibility does not equal realization.

Any model equating “many”
with “everything”
collapses into totalization.

\subsection{Known Human Paradoxes}

Counterfactual explosion \\
Decision-tree paradox \\
Option paralysis \\
Survivorship bias \\
Path dependence \\
Outcome bias \\
Historical selection bias

\subsection{Known Cosmic Constraints}

Many-worlds tension \\
Multiverse measure problem \\
Landscape problem \\
Inflationary pockets \\
$\Lambda$CDM tensions

\subsection{COP Paradox}

Branching is a continuation mode,
not an ontology of inclusion.

Total cataloguing violates admissibility.

\section{COP-03: Routed Tension, Not Resolved Conflict}

Stability is not peace.
Opposition is load-bearing.

A system survives
by routing opposing forces.

Dominance without complement
is invalid.

\subsection{Known Human Paradoxes}

Paradox of tolerance \\
Pluralism paradox \\
Functional conflict \\
Creative tension \\
Forced consensus \\
Polarization illusion

\subsection{Known Cosmic Constraints}

Entropy vs structure \\
Matter--antimatter asymmetry \\
Star formation feedback \\
Heat death tension \\
Singularity boundaries

\subsection{COP Paradox}

Stability is routed tension.

Solved conflict
is delayed collapse.

\section{COP-04: Coherence From Constraint, Not Communication}

Alignment does not require signaling.
Order does not require messengers.

Coherence is enforced
by admissibility.

If coherence requires explanation,
structure has failed.

\subsection{Known Human Paradoxes}

Hayek knowledge problem \\
Spontaneous order \\
Principal--agent problem \\
Control illusion \\
Legibility paradox \\
Coordination overhead

\subsection{Known Cosmic Constraints}

EPR paradox \\
Bell inequalities \\
Measurement problem \\
Nonlocality tension \\
Cosmic censorship

\subsection{COP Paradox}

Global coherence is enforced
by constraint, not agreement.

\section{COP-05: Experience Exists Inside a Stability Band}

Freedom is not fundamental.
Time is not guaranteed.

Complexity exists only
in protected regimes.

Outside the band,
experience vanishes.

\subsection{Known Human Paradoxes}

Freedom--security tradeoff \\
Goldilocks principle \\
Anomie \\
Social contract paradox \\
Overconstraint collapse

\subsection{Known Cosmic Constraints}

Arrow of time \\
Past hypothesis \\
Boltzmann brains \\
Anthropic banding \\
Heat death paradox \\
Inflation initial conditions

\subsection{COP Paradox}

Freedom and complexity
are emergent privileges
of the middle band.

\section{COP-06: Effects-First Ontology}

What matters most
can be invisible.

Interiors store.
Boundaries write.

Ontology follows effect.

\subsection{Known Human Paradoxes}

Streetlight effect \\
McNamara fallacy \\
Latent variables \\
Measurement bias \\
Proxy collapse

\subsection{Known Cosmic Constraints}

Dark matter \\
Dark energy \\
Missing mass \\
Horizon problem \\
Flatness problem \\
Holographic principle

\subsection{COP Paradox}

Structural legibility
outranks observability.

\section{COP-07: Unity as Frame, Plurality as Function}

Sameness destroys function.
Fragmentation destroys coherence.

Unity must be structural.
Diversity must remain real.

\subsection{Known Human Paradoxes}

Equality vs equity \\
Federalism paradox \\
Subsidiarity \\
Iron law of oligarchy \\
Role differentiation

\subsection{Known Cosmic Constraints}

$\Lambda$CDM tensions \\
Candidate proliferation \\
Measure problems \\
Landscape problem \\
Many-streams tension

\subsection{COP Paradox}

Unity constrains.
Plurality operates.

\section{COP-08: Commitment Beyond Agreement}

Consensus is not required.
Commitment replaces agreement.

Systems bind
through shared load.

\subsection{Known Human Paradoxes}

Legitimacy without consensus \\
Constitutional paradox \\
Social contract tension \\
Collective action failure

\subsection{Known Cosmic Constraints}

CPT symmetry \\
Time asymmetry \\
Two-arrow cosmology \\
Matter--antimatter symmetry

\subsection{COP Paradox}

Shared coherence persists
through binding constraints,
not shared meaning.

\section{Conclusion}

COP-00 through COP-08
define admissible continuation.

They constrain:

\begin{itemize}
  \item definition,
  \item redundancy,
  \item branching,
  \item tension,
  \item coherence,
  \item experience,
  \item ontology,
  \item unity,
  \item commitment.
\end{itemize}

Paradoxes function as boundary markers,
not problems to solve.

Together,
they form a scalable constraint system.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
