\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{S7: Structural Dissolution}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This demonstration examines structural dissolution
as the failure of constraints
that previously supported coherence and inference.
It shows how systems may persist in residual form
after invariants collapse,
and how collapse occurs when reverse narration
continues beyond structural breakdown.
No explanatory extension is proposed.
Dissolution is presented solely as constraint failure.
\end{abstract}

\section{Purpose}

This paper demonstrates a simple distinction:
when constraints fail,
legibility ends.

Its purpose is not to dramatize collapse,
but to show what becomes visible
when invariant structure disappears.

\section{What This Demonstration Is Not}

This demonstration does not:
\begin{itemize}
  \item preserve governing rules,
  \item stabilize broken frameworks,
  \item extend interpretation indefinitely,
  \item restore lost invariants,
  \item or complete explanation.
\end{itemize}

Any reading that continues inference
after constraint failure
misunderstands dissolution.

\section{What Becomes Visible}

\subsection{Failure of Invariants}

When dissolution occurs:
\begin{itemize}
  \item governing relations break,
  \item regularities disappear,
  \item predictability collapses.
\end{itemize}

Structure no longer supports mapping.

Residue remains,
but order does not.

\subsection{Why Reconstruction Fails}

Reconstruction requires invariants.
Dissolution removes them.

Nothing in unstable residue
requires that former rules
remain applicable.

Inference loses footing.

Explanation loses domain.

\section{Demonstration: Constraint Breakdown}

Consider a system
undergoing regime change.

\begin{itemize}
  \item Prior rules no longer apply.
  \item New patterns are unstable.
\end{itemize}

Old models fail.

New ones lack support.

When explanation is extended
across this boundary,
fiction emerges.

\section{How Collapse Occurs}

Collapse occurs when:
\begin{itemize}
  \item dissolved constraints are ignored,
  \item obsolete rules are retained,
  \item explanation is forced beyond domain,
  \item narration replaces structure.
\end{itemize}

Under these conditions,
analysis becomes mythology.

Limits are denied.

\section{Admissible Reading}

This demonstration permits the following reading:

\begin{quote}
After structural dissolution,
no stable invariants remain
to support reliable reconstruction or explanation.
\end{quote}

This reading preserves limits
without speculative extension.

\section{Stop Condition}

This demonstration stops at the point where:
\begin{itemize}
  \item failed frameworks are reused,
  \item inference proceeds without invariants,
  \item explanation ignores regime change,
  \item limits are denied.
\end{itemize}

Beyond this point,
dissolution collapses into fantasy.

\section{Conclusion}

Dissolution destroys structure.
Residue persists.

Rules fail.
Inference ends.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
