\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{S3: Maintenance Without History}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This demonstration examines maintenance as repetitive stabilization
that preserves present function
without preserving origin or developmental history.
It shows how systems remain viable through renewal cycles,
and how collapse occurs when upkeep is treated as archival record.
No founding narrative is proposed.
Maintenance is presented solely as structural repetition.
\end{abstract}

\section{Purpose}

This paper demonstrates a simple distinction:
repetition sustains systems
without narrating how they began.

Its purpose is not to deny past influence,
but to show what becomes visible
when continuity is maintained
without historical reference.

\section{What This Demonstration Is Not}

This demonstration does not:
\begin{itemize}
  \item document origins,
  \item preserve founding events,
  \item explain initial conditions,
  \item validate traditions,
  \item or archive beginnings.
\end{itemize}

Any reading that treats upkeep
as historical record
misunderstands its function.

\section{What Becomes Visible}

\subsection{Repetition as Structural Renewal}

When maintenance is present:
\begin{itemize}
  \item functions are restored,
  \item deviations are corrected,
  \item operation remains stable.
\end{itemize}

Cycles replace narratives.

Continuity is enacted,
not remembered.

\subsection{Why History Is Not Preserved}

History is directional.
Maintenance is cyclical.

Nothing in repetition
requires that prior states
remain represented.

Renewal proceeds
by reinstating constraints,
not by recalling origins.

\section{Demonstration: Cyclic Upkeep}

Consider a system
under regular maintenance.

\begin{itemize}
  \item Components are replaced.
  \item Performance remains constant.
\end{itemize}

Earlier configurations
disappear without trace.

When cycles are read
as evidence of intent,
routine becomes myth.

\section{How Collapse Occurs}

Collapse occurs when:
\begin{itemize}
  \item maintenance is treated as memory,
  \item repetition is moralized,
  \item tradition replaces constraint,
  \item cycles are interpreted as purpose.
\end{itemize}

Under these conditions,
stability becomes rigid.

Function yields to ritual.

\section{Admissible Reading}

This demonstration permits the following reading:

\begin{quote}
Systems remain viable
through repetitive renewal
without preserving historical origin.
\end{quote}

This reading preserves continuity
without foundational narrative.

\section{Stop Condition}

This demonstration stops at the point where:
\begin{itemize}
  \item upkeep is treated as archive,
  \item repetition becomes justification,
  \item origin stories govern practice,
  \item renewal is subordinated to memory.
\end{itemize}

Beyond this point,
maintenance collapses into tradition.

\section{Conclusion}

Maintenance preserves function.
History dissolves in cycles.

Systems renew without memory.
Origins fade.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
