\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}

\title{Caps: Structural Boundary Conditions in the COP Framework}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This document specifies the Caps of the COP framework.
Caps define non-operational structural boundary conditions.
They are not operating paradoxes and do not participate in admissible operation.
Their sole purpose is to bound the framework at entry and at return.
\end{abstract}

\section{Status and Role}

This document is not explanatory.
It is delimiting.

Caps:
\begin{itemize}
  \item are not part of the operating paradox set,
  \item are gates, not states,
  \item are not traversable as operations,
  \item and are not subject to interpretation.
\end{itemize}

Caps define where the framework may begin
and where it may return.

\section{Caps}

The COP framework contains exactly two Caps.

\subsection*{COP-00 — ALL \texttt{<->} NULL (Entry Gate)}

COP-00 bounds admissibility prior to any operation.

Operationally:
\begin{itemize}
  \item ALL is the continuity of what-can-exist,
  \item NULL is the absence of writeability,
  \item correct operation may remain non-visible.
\end{itemize}

COP-00 forbids treating visibility as priority
and forbids premature articulation.

\subsection*{ICOP-00 — 0ALL \texttt{<->} ALL (Return Gate)}

ICOP-00 bounds admissibility at return.

Operationally:
\begin{itemize}
  \item 0ALL is the explicit dissolution of distinctions,
  \item return does not preserve local histories,
  \item re-entry may carry non-local constraint signatures
        not derivable from the local forward path.
\end{itemize}

ICOP-00 forbids treating return as internal continuation
and forbids narrating re-entry as resolution.

\section{Global Notes}

\begin{itemize}
  \item Caps are not Operating Paradoxes.
  \item Caps are not Shadow Axes and are not paired.
  \item Caps do not license forward or reverse inference.
  \item Caps override all other COP sections.
\end{itemize}

\section{Placement in the COP Corpus}

Caps occupy the outermost structural layer.

They are positioned outside:
\begin{itemize}
  \item Operating Paradoxes (COP \& ICOP 1--8),
  \item Light Axes,
  \item Shadow Axes,
  \item Forbidden Moves,
  \item Extension / Non-Extension rules.
\end{itemize}

Any conflict is resolved in favor of the Caps.

\section{Use}

Caps are not used.
They are respected.

Foregrounding a Cap indicates inadmissible use.

\end{document}
