\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{Q4: ICOP-00 as Return Boundary}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This document examines ICOP-00
as the structural boundary
governing admissible return.
It shows how dissolution of distinction
regulates re-entry and re-articulation,
and how collapse occurs
when return is treated as internal continuation.
No resolution is proposed.
ICOP-00 is presented solely as a return constraint.
\end{abstract}

\section{Purpose}

This paper demonstrates a simple distinction:
return does not restore structure.

Its purpose is not to narrate endings,
but to show what becomes visible
when re-entry is constrained
by non-local dissolution.

\section{What This Demonstration Is Not}

This demonstration does not:
\begin{itemize}
  \item complete trajectories,
  \item resolve processes,
  \item restore histories,
  \item privilege outcomes,
  \item or establish closure.
\end{itemize}

Any reading that treats ICOP-00
as a terminal resolution
misunderstands its function.

\section{What Becomes Visible}

\subsection{Dissolution as Return Condition}

When ICOP-00 is operative:
\begin{itemize}
  \item local distinctions dissolve,
  \item histories are not preserved,
  \item re-entry lacks continuity.
\end{itemize}

Return occurs
without inheritance.

Structure does not reappear intact.

\subsection{Why Continuity Is Not Preserved}

Continuity is a local property.
Return is non-local.

Nothing in admissible return
requires that prior configurations
remain accessible.

Re-entry occurs
under transformed constraint.

\section{Demonstration: Non-Local Re-Entry}

Consider a system
that exits operational regimes.

\begin{itemize}
  \item Distinctions dissolve.
  \item Structure disperses.
\end{itemize}

Re-entry does not reverse this process.

When return is interpreted
as restoration,
non-locality is denied.

\section{How Collapse Occurs}

Collapse occurs when:
\begin{itemize}
  \item return is treated as continuation,
  \item histories are preserved narratively,
  \item dissolution is ignored,
  \item re-entry is idealized.
\end{itemize}

Under these conditions,
limits are overwritten.

Return becomes fiction.

\section{Admissible Reading}

This demonstration permits the following reading:

\begin{quote}
ICOP-00 constrains return
by dissolving local distinctions
and preventing restoration of prior structure.
\end{quote}

This reading preserves boundaries
without closure.

\section{Stop Condition}

This demonstration stops at the point where:
\begin{itemize}
  \item return implies restoration,
  \item re-entry is narrated as success,
  \item dissolution is denied,
  \item outcomes are privileged.
\end{itemize}

Beyond this point,
return collapses into resolution.

\section{Conclusion}

ICOP-00 bounds return.
Distinction dissolves.

Re-entry transforms.
History does not persist.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
