\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{L4: Coherence from Constraint, Not Communication}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This demonstration examines coherence as an emergent property
of shared constraint
rather than of direct communication or coordination.
It shows how systems remain globally consistent
without continuous signaling,
and how collapse occurs when coherence is made dependent on messaging.
No coordinating agent is proposed.
Coherence is presented solely as enforced compatibility.
\end{abstract}

\section{Purpose}

This paper demonstrates a simple distinction:
systems may remain coherent
through constraint
without relying on communication.

Its purpose is not to deny interaction,
but to show what becomes visible
when alignment arises from admissibility
rather than exchange.

\section{What This Demonstration Is Not}

This demonstration does not:
\begin{itemize}
  \item deny the existence of signals,
  \item oppose coordination,
  \item privilege isolation,
  \item require silence,
  \item or eliminate interaction.
\end{itemize}

Any reading that treats coherence
as dependent on constant messaging
misunderstands its basis.

\section{What Becomes Visible}

\subsection{Constraint as Coherence Generator}

When shared constraints are present:
\begin{itemize}
  \item local actions remain compatible,
  \item global patterns persist,
  \item inconsistency is filtered out.
\end{itemize}

Order arises
from restricted possibility,
not from instruction.

\subsection{Why Communication Is Not Required}

Communication is a global mechanism.
Compatibility is a local condition.

Nothing in coordinated behavior
requires continuous information exchange
if admissibility is enforced structurally.

Coherence persists
where incompatibility is excluded.

\section{Demonstration: Non-Local Alignment}

Consider a system
with distributed components
under shared constraint.

\begin{itemize}
  \item Each component operates locally.
  \item Joint outcomes remain consistent.
\end{itemize}

No component needs
full system knowledge.

When messaging is removed,
compatibility remains.

When constraint is relaxed,
communication overload appears.

\section{How Collapse Occurs}

Collapse occurs when:
\begin{itemize}
  \item coherence depends on signaling,
  \item messaging becomes mandatory,
  \item compatibility is negotiated,
  \item coordination replaces constraint.
\end{itemize}

Under these conditions,
order becomes fragile.

Noise replaces structure.

\section{Admissible Reading}

This demonstration permits the following reading:

\begin{quote}
Systems remain coherent
when shared constraints restrict joint outcomes,
without requiring continuous communication.
\end{quote}

This reading preserves alignment
without central coordination.

\section{Stop Condition}

This demonstration stops at the point where:
\begin{itemize}
  \item signaling is required for order,
  \item compatibility must be negotiated,
  \item coherence depends on consensus,
  \item structure is replaced by agreement.
\end{itemize}

Beyond this point,
coherence collapses into coordination cost.

\section{Conclusion}

Constraint enforces coherence.
Communication consumes it.

Systems align through admissibility.
Messaging is optional.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
