\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{ICOP: Inverse Core Operational Principles (00--08)}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This document presents the Inverse Core Operational Principles
(ICOP-00 through ICOP-08)
as a unified framework of reverse admissibility.
Each principle specifies structural limits
on reconstruction, inference, and legibility.
Known human and cosmic paradoxes
are mapped as diagnostic boundaries.
No hierarchy is imposed.
The principles function jointly as constraint architecture.
\end{abstract}

\section{ICOP-00: Legibility Dominance}

Reverse reading is not default.
Trace is an event.
Inference is costly.

Paradox appears only where residue
is locally visible.

Any model that assumes full reconstructability
from outcomes
violates legibility.

\subsection{Known Human Paradoxes}

Hindsight bias \\
Narrative fallacy \\
Outcome bias \\
Historian’s fallacy \\
Post-hoc rationalization \\
Confabulation \\
Just-so story bias

\subsection{Known Cosmic Constraints}

Arrow-of-time residue \\
Information loss tensions \\
Cosmic opacity \\
Horizon limits \\
Inflationary memory loss

\subsection{ICOP Paradox}

Outcomes persist.
Origins do not become legible.

Reverse inference is permitted
only within residue.

\section{ICOP-01: Residual Trace}

What remains is not what happened.
Residue is admissible.
Reconstruction is optional.

Traces are effects,
not instructions.

\subsection{Known Human Paradoxes}

Evidence paradox \\
Missing evidence fallacy \\
Survivor testimony bias \\
Artifact overinterpretation \\
Forensic overreach

\subsection{Known Cosmic Constraints}

Fossil incompleteness analogue \\
Holographic motifs \\
No-hair tension \\
Decoherence records

\subsection{ICOP Paradox}

Traces constrain stories.
Stories do not constrain traces.

\section{ICOP-02: Collapse (VEEL $\rightarrow$ 1)}

Reduction is admissible.
Recovery is not implied.

A remnant does not preserve
branching history.

\subsection{Known Human Paradoxes}

Survivorship bias \\
Path dependence \\
Winner’s curse (interpretive) \\
Institutional memory illusion \\
Outcome anchoring

\subsection{Known Cosmic Constraints}

Inflationary smoothing \\
Cosmic variance \\
Black hole evaporation \\
Phase hysteresis

\subsection{ICOP Paradox}

Collapse leaves residue.
The tree is erased.

\section{ICOP-03: Maintenance Without History}

Repetition sustains.
It does not narrate.

Stability is not memory.

Maintenance erases origin.

\subsection{Known Human Paradoxes}

Maintenance paradox \\
Prevention paradox \\
Success invisibility \\
Audit illusion \\
Broken-windows inverse

\subsection{Known Cosmic Constraints}

Entropy cycles \\
Cosmic hysteresis \\
Arrow-within-cycles tension \\
Decoherence maintenance

\subsection{ICOP Paradox}

Repetition preserves structure
while erasing explanation.

\section{ICOP-04: Decoupling}

Connectivity loss is admissible.
Disconnection encodes nothing.

Fragmentation reduces legibility.

\subsection{Known Human Paradoxes}

Breakup retrospection \\
Network archeology fallacy \\
Single-cause myth \\
Blame centralization

\subsection{Known Cosmic Constraints}

Causal horizons \\
Event horizons \\
Percolation breakdown \\
Entanglement loss

\subsection{ICOP Paradox}

When links die,
maps cannot be rebuilt.

\section{ICOP-05: Stillness}

Dynamics may halt.
Stillness is a state.

Cessation is not completion.

\subsection{Known Human Paradoxes}

Equilibrium fallacy \\
End-of-history illusion \\
Status quo bias \\
Peace-as-finality

\subsection{Known Cosmic Constraints}

Heat death motifs \\
Vacuum metastability \\
Ground-state ambiguity \\
Low-dynamics regimes

\subsection{ICOP Paradox}

Stopped processes
may remain unresolved.

\section{ICOP-06: Erasure}

Absence is admissible.
Inference from absence is not.

Erasure leaves no record.

\subsection{Known Human Paradoxes}

Argument from silence \\
Missing data bias \\
Archive illusion \\
Documentation fallacy

\subsection{Known Cosmic Constraints}

No-hair motifs \\
Information scrambling \\
Inflationary erasure \\
Cosmic censorship

\subsection{ICOP Paradox}

Erasure is real.
It is informationally silent.

\section{ICOP-07: Structural Dissolution}

Constraints can fail.
Legibility collapses.

Invariants dissolve.

\subsection{Known Human Paradoxes}

Collapse retrospection \\
Explanation illusion \\
Post-collapse mythology

\subsection{Known Cosmic Constraints}

Singularity boundaries \\
Phase transitions \\
Quantum gravity limits \\
Effective theory breakdown

\subsection{ICOP Paradox}

When rules dissolve,
the past becomes unreadable.

\section{ICOP-08: Absolute Opacity}

Some regions are unreadable.
No reconstruction is admissible.

Opacity is not hidden truth.

\subsection{Known Human Paradoxes}

Explanation compulsion \\
Origin obsession \\
Total history fantasy \\
Conspiracy completeness

\subsection{Known Cosmic Constraints}

Cosmic censorship motifs \\
Event horizon opacity \\
Pre-Big-Bang opacity \\
Observer limits

\subsection{ICOP Paradox}

Legibility can end
while existence continues.

\section{Conclusion}

ICOP-00 through ICOP-08
define reverse admissibility.

They constrain:

\begin{itemize}
  \item inference,
  \item reconstruction,
  \item narration,
  \item recovery,
  \item memory,
  \item explanation,
  \item and speculation.
\end{itemize}

Paradoxes function
as legibility boundaries.

Together,
they define the limits of reading.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
