\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{L8: Commitment Beyond Agreement}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This demonstration examines commitment as a structural relation
that enables coordinated continuation
without requiring shared interpretation or agreement.
It shows how systems remain bound
through enforced participation and shared load,
and how collapse occurs when coherence depends on aligned meaning.
No consensus is proposed.
Commitment is presented solely as structural binding.
\end{abstract}

\section{Purpose}

This paper demonstrates a simple distinction:
systems may remain coherent
through binding commitments
without shared beliefs.

Its purpose is not to eliminate disagreement,
but to show what becomes visible
when participation is enforced structurally
rather than ideologically.

\section{What This Demonstration Is Not}

This demonstration does not:
\begin{itemize}
  \item require consensus,
  \item suppress difference,
  \item privilege common values,
  \item enforce interpretation,
  \item or dissolve conflict.
\end{itemize}

Any reading that treats agreement
as necessary for cooperation
misunderstands its basis.

\section{What Becomes Visible}

\subsection{Commitment as Load-Bearing Binding}

When commitment is present:
\begin{itemize}
  \item participation is unavoidable,
  \item contribution is distributed,
  \item exit is constrained.
\end{itemize}

Binding persists
regardless of interpretation.

\subsection{Why Agreement Is Not Required}

Agreement is a semantic alignment.
Commitment is a structural condition.

Nothing in sustained cooperation
requires shared meaning
when obligations are enforced by design.

Systems persist
through constraint,
not conviction.

\section{Demonstration: Shared Infrastructure}

Consider a system
with shared supporting structures.

\begin{itemize}
  \item Participants depend on the same channels.
  \item Maintenance is jointly required.
\end{itemize}

Actors may disagree completely.

Cooperation continues
because disengagement is costly.

When binding is removed,
alignment becomes necessary.

\section{How Collapse Occurs}

Collapse occurs when:
\begin{itemize}
  \item commitment depends on belief,
  \item participation becomes voluntary,
  \item obligation is moralized,
  \item structure is replaced by persuasion.
\end{itemize}

Under these conditions,
coherence fragments.

Systems become interpretive coalitions.

\section{Admissible Reading}

This demonstration permits the following reading:

\begin{quote}
Systems may remain coherent
when participation is structurally enforced,
even in the absence of shared meaning or agreement.
\end{quote}

This reading preserves cooperation
without ideological alignment.

\section{Stop Condition}

This demonstration stops at the point where:
\begin{itemize}
  \item agreement is required for participation,
  \item commitment becomes optional,
  \item belief governs obligation,
  \item structure yields to persuasion.
\end{itemize}

Beyond this point,
coherence collapses into faction.

\section{Conclusion}

Commitment binds systems.
Agreement fluctuates.

Coherence rests on structure.
Meaning is secondary.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
