\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{L6: Effects-First Ontology}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This demonstration examines ontology as grounded in constraint effects
rather than in visible substance or internal composition.
It shows how what matters most in a system
is often expressed only through boundary impact,
and how collapse occurs when reality is equated with appearance.
No privileged interior is proposed.
Reality is presented solely as operative consequence.
\end{abstract}

\section{Purpose}

This paper demonstrates a simple distinction:
what is most real in a system
is what constrains outcomes.

Its purpose is not to deny internal structure,
but to show what becomes visible
when existence is read
through its effects.

\section{What This Demonstration Is Not}

This demonstration does not:
\begin{itemize}
  \item deny physical substance,
  \item reject internal processes,
  \item privilege surface phenomena,
  \item reduce reality to measurement,
  \item or eliminate depth.
\end{itemize}

Any reading that equates reality
with immediate visibility
misunderstands its function.

\section{What Becomes Visible}

\subsection{Boundaries as Sites of Expression}

When systems interact:
\begin{itemize}
  \item interiors store structure,
  \item boundaries transmit impact,
  \item effects register constraint.
\end{itemize}

What shapes outcomes
is what reaches the boundary.

Unexpressed structure
remains operationally silent.

\subsection{Why Appearance Is Not Decisive}

Appearance is a local display.
Constraint is a global influence.

Nothing in sustained operation
requires that decisive structure
be directly observable.

Systems are governed
by what they enforce,
not by what they show.

\section{Demonstration: Boundary Effects}

Consider a system
with hidden internal variation.

\begin{itemize}
  \item External behavior remains stable.
  \item Outcomes remain constrained.
\end{itemize}

Internal differences
matter only insofar
as they alter boundary effects.

When internal features
fail to influence interaction,
they are ontologically secondary.

\section{How Collapse Occurs}

Collapse occurs when:
\begin{itemize}
  \item visibility is treated as reality,
  \item measurement replaces constraint,
  \item proxies substitute for impact,
  \item appearance governs evaluation.
\end{itemize}

Under these conditions,
systems are misread.

Structure is replaced by display.

\section{Admissible Reading}

This demonstration permits the following reading:

\begin{quote}
What is most real in a system
is what constrains interaction and outcome,
regardless of internal visibility.
\end{quote}

This reading preserves depth
without privileging appearance.

\section{Stop Condition}

This demonstration stops at the point where:
\begin{itemize}
  \item visibility is required for reality,
  \item measurement defines existence,
  \item proxies replace constraint,
  \item surfaces override structure.
\end{itemize}

Beyond this point,
ontology collapses into representation.

\section{Conclusion}

Effects determine reality.
Appearance obscures it.

Systems are shaped at boundaries.
Interiors remain secondary.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
