\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{Q3: COP-00 as Entry Boundary}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This document examines COP-00
as the structural boundary
governing entry into admissible operation.
It shows how null dominance
regulates articulation and distinction,
and how collapse occurs
when articulation is treated as default.
No origin is proposed.
COP-00 is presented solely as an entry constraint.
\end{abstract}

\section{Purpose}

This paper demonstrates a simple distinction:
entry into operation
is not automatic.

Its purpose is not to define beginnings,
but to show what becomes visible
when articulation is constrained
by null dominance.

\section{What This Demonstration Is Not}

This demonstration does not:
\begin{itemize}
  \item identify an origin,
  \item establish first causes,
  \item privilege initial states,
  \item narrate emergence,
  \item or define foundations.
\end{itemize}

Any reading that treats COP-00
as an origin principle
misunderstands its function.

\section{What Becomes Visible}

\subsection{Null Dominance as Structural Condition}

When COP-00 is operative:
\begin{itemize}
  \item articulation is limited,
  \item distinction is costly,
  \item non-expression remains admissible.
\end{itemize}

Absence of articulation
is structurally permitted.

Visibility is optional.

\subsection{Why Articulation Is Not Default}

Articulation is a local act.
Null is a global background.

Nothing in admissible operation
requires that distinctions
be continuously produced.

Expression appears
only under constraint.

Silence remains valid.

\section{Demonstration: Constrained Entry}

Consider a system
prior to explicit differentiation.

\begin{itemize}
  \item Operations remain latent.
  \item Structure is not fully expressed.
\end{itemize}

Entry occurs
only where articulation is forced.

When articulation is assumed,
null dominance is violated.

\section{How Collapse Occurs}

Collapse occurs when:
\begin{itemize}
  \item articulation is treated as default,
  \item visibility is prioritized,
  \item distinctions are overproduced,
  \item silence is interpreted as failure.
\end{itemize}

Under these conditions,
structure saturates prematurely.

Admissibility contracts.

\section{Admissible Reading}

This demonstration permits the following reading:

\begin{quote}
COP-00 constrains entry into operation
by maintaining null dominance
over unrestricted articulation.
\end{quote}

This reading preserves entry conditions
without foundational claims.

\section{Stop Condition}

This demonstration stops at the point where:
\begin{itemize}
  \item articulation becomes mandatory,
  \item visibility is equated with existence,
  \item silence is excluded,
  \item entry is treated as automatic.
\end{itemize}

Beyond this point,
admissibility collapses into saturation.

\section{Conclusion}

COP-00 bounds entry.
Null remains dominant.

Articulation is conditional.
Silence persists.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
