\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}

\title{Shadow Axes: Admissibility Boundaries in the COP Framework}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This document specifies the Shadow Axes of the COP framework.
Shadow Axes do not extend the framework.
They bind forward admissibility to reverse legibility and exclude illegitimate inference.
This document functions as a mandatory constraint layer within the COP corpus.
\end{abstract}

\section{Status and Role}

This document is not a paper.
It is not a theory.
It is a constraint index.

The Shadow Axes:
\begin{itemize}
  \item introduce no new structure or notation,
  \item do not explain or interpret COP entries,
  \item do not form a narrative, sequence, or progression,
  \item and do not permit resolution, synthesis, or closure.
\end{itemize}

They function solely as binding constraints on how COP entries
may be read forward and diagnosed in reverse.

\section{Shadow Axes}

Each Shadow Axis binds a forward admissibility constraint
to a reverse legibility constraint.

The pairing is structural and non-negotiable.
Forward use is operational.
Reverse reading is diagnostic only.

No Shadow Axis licenses reconstruction, explanation, or control.

\subsection*{S1 — Survivability / Residue}
\textbf{COP-01 \texttt{<->} ICOP-01}

Survivability permits loss to prevent cascade.
Residue constrains inference without reconstructing events.

\textit{Boundary:}
What survives cannot preserve everything.
What remains cannot be replayed.

\subsection*{S2 — Routed Tension / Effects}
\textbf{COP-02 \texttt{<->} ICOP-02}

Routed tension permits coexistence without resolution.
Effects do not license causal reconstruction.

\textit{Boundary:}
Tension must not be resolved.
Effects must not be explained.

\subsection*{S3 — Coherence / Maintenance}
\textbf{COP-03 \texttt{<->} ICOP-03}

Coherence may persist without communication.
Maintenance is cyclic; history is not recoverable.

\textit{Boundary:}
Coherence does not imply signaling.
Upkeep does not encode origin.

\subsection*{S4 — Stability Band / Responsibility}
\textbf{COP-04 \texttt{<->} ICOP-04}

Operation is viable only within bounded ranges.
Responsibility propagates through networks, not nodes.

\textit{Boundary:}
Stability is not control.
Responsibility is not local.

\subsection*{S5 — Structural Unity / Agency}
\textbf{COP-05 \texttt{<->} ICOP-05}

One structure may support multiple distinct functions.
Agency is produced by operational conditions.

\textit{Boundary:}
Unity does not imply sameness.
Agency does not precede structure.

\subsection*{S6 — Commitment / Action}
\textbf{COP-06 \texttt{<->} ICOP-06}

Commitment stabilizes without consensus.
Only write-capable operations exist as actions.

\textit{Boundary:}
Agreement is not binding.
Intention is not action.

\subsection*{S7 — Coordinated Multiplicity / Limitation}
\textbf{COP-07 \texttt{<->} ICOP-07}

Unity arises from selective coordination.
Healthy systems require limiters.

\textit{Boundary:}
Coordination must not become total integration.
Limits must not be removed.

\subsection*{S8 — Non-Local Constraint / Unassimilable Return}
\textbf{COP-08 \texttt{<->} ICOP-08}

Forward admissibility terminates under non-local constraint.
Reverse legibility terminates in unassimilable return.

\textit{Boundary:}
What constrains articulation must not appear within it.
What returns beyond structure must not be narrated.

S8 is terminal.
It does not complete the corpus.
It prevents completion.

\section{Global Reading Discipline}

The Shadow Axes impose the following rules:

\begin{itemize}
  \item Forward use proceeds only along locally admissible operations (\texttt{+}).
  \item Reverse constraints are diagnostic only and never operational.
  \item No Shadow Axis licenses reconstruction, explanation, intervention, or closure.
  \item The configuration \texttt{--} is never locally traversed,
        but may become non-locally detectable as system non-response.
\end{itemize}

Any attempt to treat Shadow Axes as explanatory,
authoritative, or synthetic is invalid.

\section{Placement in the COP Corpus}

The COP corpus consists of layered constraint domains,
including but not limited to:

\begin{enumerate}
  \item Caps (global gates and background conditions)
  \item Operating Paradoxes (COP / ICOP loop)
  \item Shadow Axes (S1–S8)
  \item Light Axes (usable forward surfaces)
\end{enumerate}

The Shadow Axes are mandatory.
Without them, the COP list is vulnerable to illegitimate interpretation,
narrativization, and totalization.

\end{document}
