\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{L7: Unity as Frame, Plurality as Function}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This demonstration examines unity as a structural frame
that enables diverse functions
without enforcing uniformity.
It shows how systems maintain coherent accounting
while supporting differentiated roles,
and how collapse occurs when unity is confused with sameness
or plurality with fragmentation.
No universal form is proposed.
Unity is presented solely as a constraint frame.
\end{abstract}

\section{Purpose}

This paper demonstrates a simple distinction:
systems may remain unified
while sustaining functional diversity.

Its purpose is not to promote uniformity,
but to show what becomes visible
when coherence is separated
from sameness.

\section{What This Demonstration Is Not}

This demonstration does not:
\begin{itemize}
  \item enforce homogeneity,
  \item celebrate fragmentation,
  \item privilege central authority,
  \item deny specialization,
  \item or dissolve structure.
\end{itemize}

Any reading that equates unity
with uniformity
misunderstands its function.

\section{What Becomes Visible}

\subsection{Unity as Accounting Frame}

When unity is present:
\begin{itemize}
  \item interactions remain commensurable,
  \item outcomes remain comparable,
  \item coordination remains possible.
\end{itemize}

A shared frame
permits joint operation
without identical roles.

\subsection{Plurality as Operational Differentiation}

Plurality appears
as differentiated function.

\begin{itemize}
  \item Roles diverge.
  \item Capabilities specialize.
  \item Pathways diversify.
\end{itemize}

Diversity increases capacity
without dissolving coherence.

\section{Demonstration: Framed Differentiation}

Consider a system
with multiple specialized components.

\begin{itemize}
  \item Each component operates differently.
  \item All remain within a common frame.
\end{itemize}

No component represents the whole.

When specialization exceeds framing,
fragmentation appears.

When framing suppresses difference,
capability declines.

\section{How Collapse Occurs}

Collapse occurs when:
\begin{itemize}
  \item unity is enforced as sameness,
  \item diversity is allowed to detach,
  \item accounting frames diverge,
  \item coordination loses reference.
\end{itemize}

Under these conditions,
coherence disintegrates.

Function becomes incompatible.

\section{Admissible Reading}

This demonstration permits the following reading:

\begin{quote}
Systems remain coherent
when a shared frame is maintained
while functional diversity remains real.
\end{quote}

This reading preserves integration
without standardization.

\section{Stop Condition}

This demonstration stops at the point where:
\begin{itemize}
  \item difference is eliminated for order,
  \item fragmentation is normalized,
  \item frames are abandoned,
  \item coherence is sacrificed.
\end{itemize}

Beyond this point,
unity collapses into either uniformity or chaos.

\section{Conclusion}

Unity structures cooperation.
Plurality enables function.

Frames sustain diversity.
Sameness weakens systems.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
