\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{L7: Structural Visibility Under Stress}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Stable system behavior is typically invisible, while failure is highly legible.
This paper explains that asymmetry as a structural consequence of admissibility,
not as a property of observers, tools, or narratives.
Visibility arises when constraints are violated or saturated; stability disappears
into infrastructure.
\end{abstract}

\section{The Visibility Asymmetry}

Across domains, system failures attract attention while stable operation recedes
from view.
This asymmetry is often attributed to human bias or limited instrumentation.

Within the COP framework, the asymmetry is structural.
Visibility is not a feature of successful operation.
It is a consequence of constraint violation.

\section{Null Dominance}

When admissibility constraints are satisfied, they exert no visible effect.
This condition is referred to as null dominance.

Under null dominance:
\begin{itemize}
  \item operations proceed without incident,
  \item infrastructure remains backgrounded,
  \item reverse structure remains implicit.
\end{itemize}

Nothing in this state demands explanation.
As a result, stable behavior disappears from representation.

\section{Stress as a Revealing Condition}

Stress is any condition under which admissibility is challenged.
This includes saturation, boundary contact, incompatible extension, or conflicting
constraints.

Stress does not introduce new structure.
It reveals structure that was already present but inactive.

Visibility therefore correlates with constraint pressure, not with importance
or causality.

\section{Why Failure Looks Like an Event}

Failures are often narrated as discrete events.
Within the framework, they are better understood as points at which null dominance
breaks.

What appears as an event is the moment at which:
\begin{itemize}
  \item an additional operation is attempted,
  \item admissibility fails,
  \item exclusion becomes explicit.
\end{itemize}

The failure itself adds no new information.
It makes existing constraints legible.

\section{Reverse Structure and Late Legibility}

Reverse admissibility plays a central role in visibility.
Backward exclusion does not operate continuously.
It becomes legible only when incompatible histories are pruned.

As a result, reverse structure often appears suddenly,
even though it was always operative.

This produces the illusion of retrospective causation.

\section{Infrastructure and Forgetting}

Stable infrastructure is structurally forgotten.
Once an operation backgrounds successfully, it ceases to appear in further
addressing.

This forgetting is not loss.
It is a requirement for scalability.

Systems that fail to forget infrastructure remain permanently visible,
and therefore permanently brittle.

\section{Implications for Analysis}

Treating visibility as evidence of importance produces systematic error:
\begin{itemize}
  \item overfitting to failures,
  \item neglect of stable constraints,
  \item misattribution of causality.
\end{itemize}

Within the COP framework, correct analysis attends not to what is visible,
but to what must have remained admissible for visibility to occur.

\section{Relation to the COP Corpus}

This paper elaborates consequences of:
\begin{itemize}
  \item null dominance introduced in \emph{L2: A 2$\times$4$\times$8 Admissibility Framework},
  \item reading discipline specified in \emph{L3: Reading Without Reconstruction},
  \item operational behavior demonstrated in \emph{L5: Operational Admissibility in a Bounded Structure},
  \item survivability framing established in \emph{L6: The Periodic Table Is Not About Elements}.
\end{itemize}

No additional primitives are introduced.

\section{Conclusion}

Visibility is not a marker of significance.
It is a symptom of constraint pressure.

Stable systems disappear.
Failure makes structure visible.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}

