\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{S2: Collapse Without Recovery}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This demonstration examines collapse as a reduction
that preserves limited residue
without preserving branching history.
It shows how systems may survive disruption
while losing access to prior alternatives,
and how collapse occurs when survival is treated as recovery.
No restoration is proposed.
Collapse is presented solely as irreversible reduction.
\end{abstract}

\section{Purpose}

This paper demonstrates a simple distinction:
survival after collapse
does not imply recovery of what was lost.

Its purpose is not to deny persistence,
but to show what becomes visible
when reduction is separated
from restoration.

\section{What This Demonstration Is Not}

This demonstration does not:
\begin{itemize}
  \item guarantee renewal,
  \item promise resilience,
  \item preserve past options,
  \item validate winners,
  \item or justify outcomes.
\end{itemize}

Any reading that treats survival
as proof of recovery
misunderstands collapse.

\section{What Becomes Visible}

\subsection{Survivors as Non-Representatives}

When collapse occurs:
\begin{itemize}
  \item some structures remain,
  \item many alternatives disappear,
  \item selection is opaque.
\end{itemize}

What survives
does not summarize
what existed.

Residue is partial,
not exemplary.

\subsection{Why Recovery Is Not Implied}

Recovery is a forward reconstruction.
Collapse is a backward erasure.

Nothing in persistence
requires that lost paths
remain accessible.

Continuation proceeds
without restoring options.

\section{Demonstration: Post-Collapse Systems}

Consider a system
after major disruption.

\begin{itemize}
  \item Function resumes in limited form.
  \item Prior diversity is absent.
\end{itemize}

New pathways develop
under constrained conditions.

When the survivor
is treated as representative,
history is rewritten.

\section{How Collapse Occurs}

Collapse occurs when:
\begin{itemize}
  \item survival is equated with restoration,
  \item remaining structure is idealized,
  \item loss is minimized,
  \item alternatives are forgotten.
\end{itemize}

Under these conditions,
reduction is converted into narrative.

Absence becomes invisible.

\section{Admissible Reading}

This demonstration permits the following reading:

\begin{quote}
After collapse,
what remains permits continuation
without preserving access to prior alternatives.
\end{quote}

This reading preserves persistence
without recovery myths.

\section{Stop Condition}

This demonstration stops at the point where:
\begin{itemize}
  \item survival is treated as vindication,
  \item outcomes are read as optimal,
  \item loss is denied,
  \item history is reconstructed from residue.
\end{itemize}

Beyond this point,
collapse becomes legend.

\section{Conclusion}

Collapse reduces systems.
Survival narrows them.

What remains is partial.
Recovery is not guaranteed.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
