\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{Q5: Light Work as Operational Surface}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This document examines the Light work
as the forward-facing operational surface
of the COP framework.
It shows how the Light series
provides usable constraint interfaces
without authorizing interpretation,
and how collapse occurs
when Light is treated as guidance or doctrine.
No methodology is proposed.
Light work is presented solely as an admissible surface.
\end{abstract}

\section{Purpose}

This paper demonstrates a simple distinction:
Light work enables operation
without providing explanation.

Its purpose is not to instruct practice,
but to show what becomes visible
when forward use is constrained
by admissibility rather than meaning.

\section{What This Demonstration Is Not}

This demonstration does not:
\begin{itemize}
  \item prescribe action,
  \item define best practices,
  \item authorize decisions,
  \item provide models,
  \item or supply justification.
\end{itemize}

Any reading that treats Light work
as methodological guidance
misunderstands its role.

\section{What Becomes Visible}

\subsection{Light as Usable Interface}

When Light work is operative:
\begin{itemize}
  \item constraints are accessible,
  \item forward moves are bounded,
  \item illegitimate operations are filtered.
\end{itemize}

The Light papers
do not explain structure.

They expose
where operation remains admissible.

\subsection{Why Instruction Is Not Provided}

Instruction is a normative act.
Constraint is a structural condition.

Nothing in admissible operation
requires prescriptive guidance.

Use proceeds
by exclusion,
not by recommendation.

\section{Demonstration: Forward Filtering}

Consider a system
operating within COP constraints.

\begin{itemize}
  \item Some actions remain viable.
  \item Others are excluded.
\end{itemize}

No preferred path is selected.

Only admissibility
is evaluated.

When Light is treated
as a manual,
constraint becomes authority.

\section{How Collapse Occurs}

Collapse occurs when:
\begin{itemize}
  \item Light is used as instruction,
  \item operational surfaces become rules,
  \item constraints are moralized,
  \item usability becomes legitimacy.
\end{itemize}

Under these conditions,
the framework becomes procedural.

Structure is replaced by technique.

\section{Admissible Reading}

This demonstration permits the following reading:

\begin{quote}
The Light series functions
as a usable surface for forward operation
without prescribing interpretation or action.
\end{quote}

This reading preserves usability
without authority.

\section{Stop Condition}

This demonstration stops at the point where:
\begin{itemize}
  \item Light is treated as guidance,
  \item procedures are extracted,
  \item legitimacy is inferred from use,
  \item operation becomes doctrine.
\end{itemize}

Beyond this point,
Light collapses into method.

\section{Conclusion}

Light enables use.
It does not instruct.

Constraints filter action.
Meaning remains external.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
