\input{../../../templates/arxiv/arxiv.tex}
\usepackage{../../../templates/cop/cop-macros}
\usepackage{../../../templates/cop/cop-diagrams}

\title{Q6: Shadow Work as Diagnostic Boundary}
\author{Pascal Sparidaens}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This document examines the Shadow work
as the reverse-facing diagnostic boundary
of the COP framework.
It shows how the Shadow series
marks limits of reconstruction and inference
without authorizing negation or critique,
and how collapse occurs
when Shadow is treated as debunking or authority.
No evaluative stance is proposed.
Shadow work is presented solely as a boundary surface.
\end{abstract}

\section{Purpose}

This paper demonstrates a simple distinction:
Shadow work marks limits of legibility
without invalidating forward operation.

Its purpose is not to criticize practice,
but to show what becomes visible
when reverse reading is constrained
by admissibility.

\section{What This Demonstration Is Not}

This demonstration does not:
\begin{itemize}
  \item invalidate systems,
  \item promote skepticism,
  \item authorize critique,
  \item justify disengagement,
  \item or establish superiority.
\end{itemize}

Any reading that treats Shadow work
as evaluative or dismissive
misunderstands its role.

\section{What Becomes Visible}

\subsection{Shadow as Boundary Interface}

When Shadow work is operative:
\begin{itemize}
  \item illegible reconstructions are excluded,
  \item narrative overreach is blocked,
  \item speculative histories are filtered.
\end{itemize}

The Shadow papers
do not negate structure.

They expose
where structure cannot be recovered.

\subsection{Why Judgment Is Not Provided}

Judgment is a normative act.
Diagnosis is a structural act.

Nothing in admissible legibility
requires evaluative stance.

Boundaries function
by termination,
not by appraisal.

\section{Demonstration: Reverse Screening}

Consider a system
with partial residue.

\begin{itemize}
  \item Some interpretations remain bounded.
  \item Others are excluded.
\end{itemize}

No position is endorsed.

Only legibility
is evaluated.

When Shadow is treated
as critique,
constraint becomes posture.

\section{How Collapse Occurs}

Collapse occurs when:
\begin{itemize}
  \item Shadow is used to dismiss systems,
  \item boundaries become accusations,
  \item opacity is moralized,
  \item limits are politicized.
\end{itemize}

Under these conditions,
diagnosis becomes ideology.

Structure is replaced by stance.

\section{Admissible Reading}

This demonstration permits the following reading:

\begin{quote}
The Shadow series functions
as a diagnostic boundary
marking limits of reconstruction and inference
without authorizing judgment or negation.
\end{quote}

This reading preserves limits
without hierarchy.

\section{Stop Condition}

This demonstration stops at the point where:
\begin{itemize}
  \item boundaries are used as weapons,
  \item opacity becomes accusation,
  \item diagnosis becomes critique,
  \item limits become identity.
\end{itemize}

Beyond this point,
Shadow collapses into posture.

\section{Conclusion}

Shadow marks limits.
It does not judge.

Diagnosis constrains reading.
Meaning remains external.

Nothing further is claimed.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
